% An example for the ar2rc document class.
% Copyright (C) 2017 Martin Schroen
% Modifications Copyright (C) 2020 Kaishuo Zhang
% Further Modifications Copyright (C) 2022 Hayato Itoh 
%
% This program is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <http://www.gnu.org/licenses/>.

\documentclass{ar2rc}
\pagestyle{myheadings}
\title{Submission ID ``Manuscript's Title''}
%\author{}
%\journal{}
%\doi{}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}


\begin{document}
October 7, 2023\\
\\
\\
\maketitle
\vskip0.5\baselineskip
Dear Editor and Reviewers: 
\vskip0.5\baselineskip
Thank you very much for reviewing our manuscript titled Manuscript's Title submitted to {\it Journal's name}. 
We are writing this response letter to resubmit our revised manuscript for your further consideration. 
We have made significant changes based on the valuable comments provided by the reviewers.
We respond to each reviewer's comments in detail below.
\vskip0.5\baselineskip
Yours sincerely, \\ 
Author's name
\clearpage

\section{Reviewer \#1}
\subsection*{}
\RC  The paper aims to define a new Hoge for Fuga. However, the author may have misunderstood the Fuga. 

\AR Thank you for the review comments. We have refined the definition of Fuga and added descriptions to improve the manuscript's readability.


\subsection*{}
\RC  This manuscript misses an important explanation. 

\AR In the revised manuscript, we have added the following sentence. 
\begin{quote}
 Nerver for Ever For Ever Never.\\ 
(Page 7, right column, lines 7-11)
\end{quote}


\section{Reviewer \#2}
\subsection*{}
\RC  The file name includes a typo.

\AR  We revised the name of our example tex file.




\end{document}
